### 2016-08-26 section/1_under.tex
address linhai comments

Previous work identified a wide variety of performance root-cause 
categories. However, existing taxonomies do not satisfy all these 
requirements and hence cannot be directly used by us.
Therefore, we have designed our own taxonomy,
as presented below.
We will discuss how our taxonomy meets these three requirements
qualitatively in this section and quantitatively 
using real-world performance-bug suite in Section \ref{sec:eval_taxonomy}.

>>>>

Previous work identified a wide variety of performance root-cause 
categories. However, existing taxonomies do not satisfy all these 
requirements and hence cannot be directly used by us.
Therefore, we have designed our own taxonomy,
as presented below.
We will discuss how our taxonomy meets these three requirements
qualitatively in this section and quantitatively 
using real-world performance bugs in Section \ref{sec:eval_taxonomy}.

### 2016-08-26 section/5_exper.tex
address linhai comments

The accuracy of \Tool benefits from its run-time analysis.
%{\color{red} For example, there are 26 
For example, our run-time analysis has correctly pruned out 24 false positives
in 0*1? inefficiency detection for our benchmarks. Each of these 24 loops is a
top-5 suspicious loops in one of our benchmarks; it only generates side effects
in its last iteration, and hence is identified as 0*1? by static analysis. 
Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the number of iterations of each loop instance and
correctly identifies them as false positives. Similarly, \Tool run-time analysis
helps prune out 19 false positives for [0$|$1]* loop identification.

>>>>

The accuracy of \Tool benefits from its run-time analysis.
%{\color{red} For example, there are 26 
For example, our run-time analysis has correctly pruned out 24 false positives
in 0*1? inefficiency detection for our benchmarks. Each of these 24 loops is a
top-5 suspicious loop in one of our benchmarks; it only generates side effects
in its last iteration, and hence is identified as 0*1? by static analysis. 
Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the number of iterations of each loop instance and
correctly identifies them as false positives. Similarly, \Tool run-time analysis
helps prune out 19 false positives for [0$|$1]* loop identification.
